Climate efficiency

### 2022-04-29 Paper.Rmd
Updated the RMD file (new NASS data, broken code into chunks)

$$ y_t  = \alpha_0 + \alpha_1 y_t$$
where ${{\alpha }_{1}}$ is the county yield intercept, $f\left( t \right)$ is the county’s estimated yield trend through time and ${{\varepsilon }_{t}}$ is the county’s residual yield variation. The following set of linear or nonlinear functional form of $f\left( t \right)$ is evaluated:

@@

We obtained the crops data...

```{r prepare-crops-data, cache=cache, echo = FALSE}

# Specify the date-dependent component of the data file name
yrdd='20211223'

# Download the file
download.file(sprintf('ftp://ftp.nass.usda.gov/quickstats/qs.crops_%s.txt.gz',yrdd),sprintf('qs.crops_%s.txt.gz',yrdd), mode='wb')

# Read the file into an object
ss= read.csv(sprintf('qs.crops_%s.txt.gz',yrdd), sep='\t')

# Replace STATE_ANSI with 99 for US TOTALS
ss$STATE_ANSI = ifelse(ss$STATE_NAME=='US TOTAL',99,ss$STATE_ANSI)

# Subset only needed data into object SS1
ss1 = ss[ss$SOURCE_DESC %in% c('SURVEY') &
           ss$STATISTICCAT_DESC %in% c('AREA HARVESTED',
                                       'AREA PLANTED',
                                       'AREA PLANTED, NET',
                                       'PRICE RECEIVED',
                                       'PRODUCTION',
                                       'YIELD',
                                       'STOCKS',
                                       'SALES') & 
           ss$AGG_LEVEL_DESC %in% c('NATIONAL',
                                    'STATE',
                                    'AGRICULTURAL DISTRICT',
                                    'COUNTY') & 
           ss$FREQ_DESC %in% c('ANNUAL',
                               'MONTHLY',
                               'POINT IN TIME') &
           ss$REFERENCE_PERIOD_DESC %in% c('MARKETING YEAR','YEAR',
                                           'JAN','FEB','MAR','APR','MAY','JUN',
                                           'JUL','AUG','SEP','OCT','NOV','DEC',
                                           'FIRST OF DEC','FIRST OF JUN',
                                           'FIRST OF MAR','FIRST OF SEP') & 
           !ss$UNIT_DESC %in% c('OPERATIONS',
                                'PCT',
                                'PCT BY COLOR',
                                'PCT BY GRADE',
                                'PCT BY SIZE GROUP',
                                'PCT BY TYPE',

@@

# Values contain illegal commas--only extract the numerals and turn the column into numeric
ss1$VALUE_num <- as.numeric(gsub('[^0-9\\.]','',ss1$VALUE, perl = TRUE))

# Remove all silage
ss1=ss1[!ss1$UTIL_PRACTICE_DESC %in% c('SILAGE','FORAGE'),]

ss1$UTIL_PRACTICE_DESC = ifelse(ss1$COMMODITY_DESC
                               %in% c('CORN','SORGHUM'),'GRAIN',
                               ss$UTIL_PRACTICE_DESC)

# Define mappings
mapping = list(
  'FOOD GRAINS' = c('RICE', 'RYE', 'WHEAT'),
  'FEED CROPS' = c(
    'BARLEY',
    'CORN',
    'HAY',
    'MILLET',
    'OATS',
    'PROSO MILLET',
    'SORGHUM'
  ),
  'FIBER' = c(
    'COTTON',
    'COTTON LINT',
    'COTTON LINT, LONG STAPLE',
    'COTTON LINT, UPLAND',
    'COTTONSEED'
  ),
  TOBACCO = 'TOBACCO',
  'OIL CROPS' = c(
    'CAMELINA',
    'CANOLA',
    'FLAXSEED',
    'MISCELLANEOUS OIL CROPS',
    'MUSTARD',
    'MUSTARD SEED',
    'PEANUTS',
    'RAPESEED',
    'SAFFLOWER',
    'SOYBEANS',
    'SUNFLOWER'
  ),

@@

ss1$COMMODITY_GROUP = mappingVector[ss1$COMMODITY_DESC]

@@

countyData=countyData[countyData$COMMODITY_DESC=='CORN',]

>>>>

@@

We obtained the crops data from NASS QuickStats:

```{r load-data, cache=cache, echo = TRUE}
# Specify the date-dependent component of the data file name
yrdd='20220428'

# Download the file
download.file(
  sprintf('ftp://ftp.nass.usda.gov/quickstats/qs.crops_%s.txt.gz',yrdd),
  sprintf('qs.crops_%s.txt.gz',yrdd), 
  mode='wb'
)

# Read the file into an object
ss= read.csv(sprintf('qs.crops_%s.txt.gz',yrdd), sep='\t')
```

In the first step we only keep the survey data for six     variables at national, state, ag. district and county level, excluding percentage point changes. We also exclude the data for "other counties" and "other states" which includes data that is protected.

```{r prepare-crops-data, cache=cache, echo = TRUE}
# Subset only needed data into object SS1
ss1 = ss[ss$SOURCE_DESC %in% c('SURVEY') &
           ss$STATISTICCAT_DESC %in% c('AREA HARVESTED',
                                       'AREA PLANTED',
                                       'PRICE RECEIVED',
                                       'PRODUCTION',
                                       'YIELD',
                                       'STOCKS') &
           ss$AGG_LEVEL_DESC %in% c('NATIONAL',
                                    'STATE',
                                    'AGRICULTURAL DISTRICT',
                                    'COUNTY') &
           ss$FREQ_DESC %in% c('ANNUAL',
                               'MONTHLY',
                               'POINT IN TIME') &
           ss$REFERENCE_PERIOD_DESC %in% c('MARKETING YEAR','YEAR',
                                           'JAN','FEB','MAR','APR','MAY','JUN',
                                           'JUL','AUG','SEP','OCT','NOV','DEC',
                                           'FIRST OF DEC','FIRST OF JUN',
                                           'FIRST OF MAR','FIRST OF SEP') &
           !ss$UNIT_DESC %in% c('OPERATIONS',
                                'PCT',
                                'PCT BY COLOR',
                                'PCT BY GRADE',
                                'PCT BY SIZE GROUP',
                                'PCT BY TYPE',

@@

ss1$STATISTICCAT_DESC = ifelse(ss1$STATISTICCAT_DESC %in% c('PRODUCTION') & ss1$UNIT_DESC %in% c('$', '$ / TON', '$, CHERRY BASIS','$, ON TREE EQUIV', '$, PHD EQUIV'), 'REVENUE', ss1$STATISTICCAT_DESC)
```

```{r character-values-to-numbers, cache=cache, echo = FALSE}
# Values contain illegal commas--only extract the numerals and turn the column into numeric
ss1$VALUE_num <- as.numeric(gsub('[^0-9\\.]','',ss1$VALUE, perl = TRUE))
```

```{r fix-county-names, cache=cache, echo = FALSE}

ss1$COUNTY_NAME = ifelse(ss1$CONTY_NAME=='ST. JOSEPH', 'ST JOSEPH', ss1$COUNTRY_NAME)
ss1$COUNTY_NAME = ifelse(ss1$CONTY_NAME=='ST. LOUIS', 'ST LOUIS', ss1$COUNTRY_NAME)
ss1$COUNTY_NAME = ifelse(ss1$CONTY_NAME=='ST. JOHN THE BAPTIST', 'ST JOHN THE BAPTIST', ss1$COUNTRY_NAME)
ss1$COUNTY_NAME = ifelse(ss1$CONTY_NAME=='ST. JOHNS', 'ST JOHNS', ss1$COUNTRY_NAME)
ss1$COUNTY_NAME = ifelse(ss1$CONTY_NAME=='ST. LUCIE', 'ST LUCIE', ss1$COUNTRY_NAME)
ss1$COUNTY_NAME = ifelse(ss1$CONTY_NAME=='STE. GENEVIEVE', 'STE GENEVIEVE', ss1$COUNTRY_NAME)
```

```{r eliminate-totals, cache = cahce, echo = TRUE}

ss1 = ss1[!ss1$COMMODITY_DESC %in% c('BEDDING PLANT TOTALS','BERRY TOTALS','CITRUS TOTALS',
'CROP TOTALS','FIELD CROP & VEGETABLE TOTALS',
'FIELD CROP TOTALS','FLORICULTURE TOTALS',
'FOOD CROP TOTALS','FRUIT & TREE NUT TOTALS',
'FRUIT TOTALS','GRASSES & LEGUMES TOTALS','HORTICULTURE TOTALS',
'NON-CITRUS FRUIT & TREE NUTS TOTALS','NON-CITRUS TOTALS',
'NURSERY TOTALS','TREE NUT TOTALS','VEGETABLE TOTALS'), ]
```

```{r remove-silage, cache=cache, echo = TRUE}
# Remove all silage
ss1=ss1[!ss1$UTIL_PRACTICE_DESC %in% c('SILAGE','FORAGE'),]
```

```{r correct-utilization, cache=cache, echo = TRUE}
ss1$UTIL_PRACTICE_DESC = ifelse(ss1$COMMODITY_DESC
                               %in% c('CORN','SORGHUM'),'GRAIN',
                               ss$UTIL_PRACTICE_DESC)
```

```{r remove-silage, cache=cache, echo = TRUE}
# Define mappings
mapping = list(
  'FOOD GRAINS' = c('RICE', 'RYE', 'WHEAT'),
  'FEED CROPS' = c(
    'BARLEY',
    'CORN',
    'HAY',
    'MILLET',
    'OATS',
    'PROSO MILLET',
    'SORGHUM'
  ),
  'FIBER' = c(
    'COTTON',
    'COTTON LINT',
    'COTTON LINT, LONG STAPLE',
    'COTTON LINT, UPLAND',
    'COTTONSEED'
  ),
  TOBACCO = 'TOBACCO',
  'OIL CROPS' = c(
    'CAMELINA',
    'CANOLA',
    'FLAXSEED',
    'MISCELLANEOUS OIL CROPS',
    'MUSTARD',
    'MUSTARD SEED',
    'PEANUTS',
    'RAPESEED',
    'SAFFLOWER',
    'SOYBEANS',
    'SUNFLOWER'
  ),

@@

ss1$COMMODITY_GROUP = mappingVector[ss1$COMMODITY_DESC]
```

```{r extract-non-price-data, cache=cache, echo = TRUE}

@@

#countyData=countyData[countyData$COMMODITY_DESC=='CORN',]
